\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-10 paper/ms.tex
Dan's logH comment

For convenience later on, we 
separate the prior and proposal-related terms from
the likelihood-related term, and write the former as
\begin{align}
H = \frac{q(\params'|\params)}{q(\params | \params')}
\times \frac{\pi(\params')}{\pi(\params)}
\end{align}
so the acceptance probability becomes
\begin{align}
\alpha &= \min\left[1,
H\times
\mathds{1}\left(L(\params') > \ell_j\right)
\right]
\end{align}

@@

The class must also define and implement the following member functions:
\begin{enumerate}[(i)]
\item \code{void from\_prior(DNest4::RNG\& rng)}, which generates parameter
        values from the prior;
\item \code{double perturb(DNest4::RNG\& rng)}, which proposes a
        change to the parameter values, and returns $\ln(H)$ as defined in
        Equation~\ref{eqn:log_hastings};
\item \code{double log\_likelihood() const}, which evaluates the log of
        the likelihood function;
\item \code{void print(std::ostream\& out) const}, which prints parameters of
        interest to the given output stream; and
\item \code{std::string description() const}, which returns a \proglang{C++}
        string naming the parameters printed by \code{print(std::ostream\&) const}.
        This string is printed (after a comment character \#) at the top of
        the output file.
\end{enumerate}
These are all described (using the linear regression example) in the
following subsections.

@@

\subsection{Proposal moves}
The \code{perturb} member function for the straight line model is:
\begin{CodeChunk}
\begin{CodeInput}
double StraightLine::perturb(DNest4::RNG& rng)
{
    double log_H = 0.0;

@@

This first chooses a random integer from $\{0, 1, 2\}$ using the
\code{rand\_int(int)} member function of the \code{DNest4::RNG} class.
This determines which of the three parameters
$(m, b, \sigma)$ is modified. In this example, there are no proposals
that modify more than one of the parameters at a time, and all proposals
are ``random walk'' proposals that add a perturbation
(drawn from a symmetric distribution) to the current value.

\subsection{Proposals for single parameters}
The proposal for $m$ involves adding a perturbation to the current
value using the line

>>>>

For convenience later on, we 
separate the prior and proposal-related terms from
the likelihood-related term, and write the former as
\begin{align}
H = \frac{q(\params'|\params)}{q(\params | \params')}
\times \frac{\pi(\params')}{\pi(\params)}.
\end{align}

The logarithm of $H$,
\begin{align}
\ln(H) = \ln\left[\frac{q(\params'|\params)}{q(\params | \params')}
\times \frac{\pi(\params')}{\pi(\params)}\right],
\end{align}
is the user's responsibility when implementing models,
and will become relevant in Sections~\ref{sec:perturb}
and~\ref{sec:proposals}.
In terms of $\ln(H)$, the
acceptance probability becomes
\begin{align}
\alpha &= \min\left[1,
e^{\ln(H)}\times
\mathds{1}\left(L(\params') > \ell_j\right)
\right].\label{eqn:logH}
\end{align}

@@

The class must also define and implement the following member functions:
\begin{enumerate}[(i)]
\item \code{void from\_prior(DNest4::RNG\& rng)}, which generates parameter
        values from the prior;
\item \code{double perturb(DNest4::RNG\& rng)}, which proposes a
        change to the parameter values, and returns $\ln(H)$ as defined in
        Equation~\ref{eqn:logH};
\item \code{double log\_likelihood() const}, which evaluates the log of
        the likelihood function;
\item \code{void print(std::ostream\& out) const}, which prints parameters of
        interest to the given output stream; and
\item \code{std::string description() const}, which returns a \proglang{C++}
        string naming the parameters printed by \code{print(std::ostream\&) const}.
        This string is printed (after a comment character \#) at the top of
        the output file.
\end{enumerate}
These are all described (using the linear regression example) in the
following subsections.

@@

\subsection{Proposal moves}\label{sec:perturb}
The \code{perturb} member function for the straight line model is given below.
This takes a random number generator as input, makes changes to
a subset of the parameters, and returns a \code{double} corresponding
to $\ln(H)$ as defined in Equation~\ref{eqn:logH}. The combination of
the choice of proposal and the $\ln(H)$ value returned must be consistent
with the prior distribution.
\begin{CodeChunk}
\begin{CodeInput}
double StraightLine::perturb(DNest4::RNG& rng)
{
    // log_H value to be returned
    double log_H = 0.0;

@@

This function first chooses a random integer from $\{0, 1, 2\}$ using the
\code{rand\_int(int)} member function of the \code{DNest4::RNG} class.
This determines which of the three parameters
$(m, b, \sigma)$ is modified. In this example, there are no proposals
that modify more than one of the parameters at a time, and all proposals
are ``random walk'' proposals that add a perturbation
(drawn from a symmetric distribution) to the current value.

\subsection{Proposals for single parameters}\label{sec:proposals}
The proposal for $m$ involves adding a perturbation to the current
value using the line
